\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-06-20 Manuscript/reply.tex
explained more stuff and responded to comments

The heat effect measures the speed-level of the heat.  We added some additional
explanations to make it clear what the venue and heat effect refer to.

@@

Can be removed.

@@

Yes, this can be easily resolved.

@@

This was meant to be used as further evidence to show 2022 is an outlier. Perhaps
we delete this graph? I am unsure what the reviewer means by where "2022 stands
in the distribution"

>>>>

The heat effect measures the speed-level of the heat.  We added some additional
explanations to make it clear what the venue and heat effect refer to. We did
not want to call it a "race effect" as we were worried that may be interpreted
to mean the race of the athlete.

@@

Yes, the comments about the difficulty of data gathering are meant to demostrate
that we worked hard to find as much data as we could and as a note to World
Athletics (track and field governing body) that they need to do a better job
at data standardization.  Currently the races on their website do not include
reaction times, which meant that we had to look in alternative places to perform
the analysis that we did.

@@

Yes, this has been resolved.

@@

We included this plot to show the venue effect for each year and to visually
demonstrate how 2022 compares to other years.  We added additional comments
about the probability of observing an extreme venue effect to provide
quantitative data supporting our argument.
